---
title: "Assignment 5"
author: "Nathan and Sydney"
format: html
editor: visual
---

# Metal Recycling Program

Workflow:

1.  Cost of Electricity (S)

2.  Metal Production (S)

3.  Collection (S)

4.  Recycling (N)

5.  Waste (N)

6.  Metal Switching (N)

## Setup

```{r}
# clear the environment
rm(list = ls())

```

```{r}
# load needed libraries
library(here)
```

# Main Program

## Create Vectors

For electricity cost to influence the production and recycling rates, we could create a random uniform distribution with electricity costs, that then ranks them as high or low depending on the value of the output – for it to influence production and recycling, it would need to go first.

- Range 10-30 cents/kWh (based on average electricity costs)

- The function determines high vs low and reports that value and score

  - High = equal to or above 16 cents/kWh

  - Low = below 16 cents/kWh

# Modules

### Module 1: Cost of Electricity

- **I had to put this first so that it actually influences the production and recycling rates**

```{r}

source(here("modules/electricity_cost.R"))

# default is a random scenario, but can be changed
electricity_rates<- cost_of_electric(1,"Tuesday")
electricity_rates


# this can be run for multiple days -- right now it's set to have the highest electricity costs during months, 6, 7, and 8 as well as during the weekdays. 

## weekends have a 50% discount on electricity

```

### **Run the Electricity module 2x - choose weekend or weekday**

**Weekend**

```{r}
#### THIS MODULE NEEDS TO RUN TWICE
cheap_electricity<- cost_of_electric(6,"Saturday")

electricity_rates <- cheap_electricity
```

**Weekday**

```{r}
expensive_electricity<- cost_of_electric(1,"Tuesday")

electricity_rates <- expensive_electricity
```

### Metal Ore Data frame

```{r}

# make a dataframe with metal ore information

metal <- c("steel", "aluminum", "copper")

metal_ore <- data.frame(
  metal = metal,
  mass = runif(length(metal), 1, 100),
  
  # I chose random percentages for the collection rates
  collection_rate = (c(0.95, 0.7, 0.5))
)

# production rate depends on electricity
metal_ore$production_rate <- ifelse(
  electricity_rates$electricity == "high",
  runif(length(metal), 0, 0.5),
  runif(length(metal), 0.6, 1)
)

# recycling rate depends on electricity
metal_ore$recycling_rate <- ifelse(
  electricity_rates$electricity == "high",
  runif(length(metal), 0, 0.5),
  runif(length(metal), 0.6, 1)
)

# return the ore information and the electricity rates for context
metal_ore
electricity_rates

```

## Initialize Values

I had to initialize recycling so that metal production eventually knows what to add once it goes through the next iterations.

```{r}

# initialize recyling value
recycled_metal<- 0

```

### Module 2: Metal Production

```{r}

# call the metal production module
source(here("modules/metal_production.R"))

## run it
produced_metal<- metal_production(metal_ore$mass, 
                                 recycled_metal, 
                                 metal_ore$production_rate)
data.frame(
  metal= metal, 
  produced_metal
)

```

### Module 3: Collection

```{r}
# collection
source(here("modules/collection_scrap.R"))

## run it
collected_scrap<- collection_scrap(produced_metal,
                                   metal_ore$collection_rate)

data.frame(
  metal= metal, 
  collected_scrap
)

```

### Module 4: Recycling

```{r}
# recycling
source(here("modules/scrap_recycling.R"))

## run it
recycled_metal <- scrap_recycling(collected_scrap, 
                          metal_ore$recycling_rate)

data.frame(
  metal = metal,
  recycled_metal
)
```

### Module 5: Waste

```{r}
# waste
source(here("modules/waste_loss.R"))

## run it
waste <- waste_loss(produced_metal, 
                    metal_ore$collection_rate,
                    recycled_metal,
                    metal_ore$recycling_rate,
                    metal_ore$mass)

data.frame(
  metal = metal,
  waste
)

```

### Module 6: Metal Switching Module

```{r}
# metal switching
source(here("modules/metal_switching.R"))

```
