---
title: "Assignment 5"
author: "Nathan and Sydney"
format: html
editor: visual
---

# Metal Recycling Program

Workflow:

1.  Metal Production (S)

2.  Collection (S)

3.  Recycling (N)

4.  Waste (N)

5.  Cost of Electricity (S)

6.  Metal Switching (N)

## Setup

```{r}
# clear the environment
rm(list = ls())

```

```{r}
# load needed libraries
library(here)
```

# Main Program

## Create Vectors

For electricity cost to influence the production and recycling rates, we could create a random uniform distribution with electricity costs, that then ranks them as high or low depending on the value of the output – for it to influence production and recycling, it would need to go first.

- Range 10-30 cents/kWh (based on average electricity costs)

- The function determines high vs low and reports that value and score

  - High = equal to or above 16 cents/kWh

  - Low = below 16 cents/kWh

### Module 1: Cost of Electricity

- there need to be more clear inputs if this is going to work as a function

- ok I'll get rid of the for loop and instead have specified scenarios for different days and times

```{r}

source(here("modules/electricity_cost.R"))

electricity_rates<- cost_of_electric(1,"Tuesday")

electricity_rates
```

### Metal Ore Data frame

```{r}

# make a dataframe with metal ore information
## we don't need to keep this, I just used it for testing


# make different parts of the dataframe based on if electricity is high or low

# named the different metal types
metal= c("steel","aluminum","copper")

# made a dataframe for metal ore
metal_ore<- data.frame(
  
  # metal row is the names of the metal types
  metal=metal,
  
  # mass is how much metal is extracted, and is randomized between 1 and 100 MT
  mass = runif(length(metal), 1,100),
  
  # p
  production_rate = runif(length(metal), 0,1),
  recycling_rate = runif(length(metal), 0,1),
  collection_rate = runif(length(metal), 0,1),
  electricity_cost = runif(length(metal), 0,100)
)

############ TRYING TO VARY THINGS BASED ON THE RATES
# named the different metal types
metal= c("steel","aluminum","copper")

# made a data frame for metal ore
metal_ore<- data.frame(
  
  # metal row is the names of the metal types
  metal=metal,
  
  # mass is how much metal is extracted, and is randomized between 1 and 100 MT
  mass = runif(length(metal), 1,100),
  
# production rate on a high electricity day
if (electricity == "high") {
production_rate = runif(length(metal), 0,0.5)},

# production rate on a low electricity day
if (electricity == "low") {
  production_rate = runif(length(metal), 0.6,1)},

if (electricity == "high") {
# recycling rate on a high electricity day
  recycling_rate = runif(length(metal), 0,1)},

if (electricity == "low") {
  # recycling rate on a high electricity day
  recycling_rate = runif(length(metal), 0,1)},

# collection rate stays the same
  collection_rate = runif(length(metal), 0,1),
)



```

## Initialize Values

```{r}

# initialize recyling value
recycled_metal<- 0

```

## Modules

### Module 1: Metal Production

```{r}

# call the metal production module
source(here("modules/metal_production.R"))

## run it
produced_metal<- metal_production(metal_ore$mass[1], 
                                 recycled_metal, 
                                 metal_ore$production_rate[1])
produced_metal

```

### Module 2: Collection

```{r}
# collection
source(here("modules/collection_scrap.R"))

# uniform distribution between 10 and 30 cents/kwh 

# if statement, if above 16, then high, otherwise, low

# if high use low production and recycling, if low use high production and recycling

## run it
collected_scrap<- collection_scrap(produced_metal,
                                   metal_ore$collection_rate[1])

collected_scrap
```

### Module 3: Recycling

```{r}
# recycling
source(here())
```

### Module 4: Waste

```{r}
# waste
source(here())

```

### Module 5: Cost of Electricity

```{r}
# cost of electricity
source(here())

```

### Module 6: Metal Switching Module

```{r}
# metal switching
source(here())

```
